Automated discovery of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Update ms.tex

Although we focus on GW in this work, the method can be easily extended to other population analysis.
For example, given the recently release Gaia DR3 data \cite{2016A&A...595A...1G}, , we can apply our method to understanding the population of stars without much augmentation to the pipeline.
As size of data sets grows larger in astronomy, this work provides a simple and scalable pathway to uncover trends and relations in astrophysical catalogs.

>>>>

Although we focus on GW in this work, the method can be easily extended to other population analysis.
For example, given the recently release Gaia DR3 data \cite{Collaboration2016TheGM}, we can apply our method to understanding the population of stars without much augmentation to the pipeline.
As size of data sets grows larger in astronomy, this work provides a simple and scalable pathway to uncover trends and relations in astrophysical catalogs.
